---
title: "Latent change score models"
---

```{r setup, verbose = FALSE, warning = FALSE, message = FALSE}
source("T1_plus_T3-datasetup.R")
```

```{r univariate-model}
#This script is adapted from the manuscript 
#'Developmental cognitive neuroscience using Latent Change Score models: A tutorial and applications'
#Rogier A. Kievit, Andreas M. Brandmaier, Gabriel Ziegler, Anne-Laura van Harmelen, 
#Susanne de Mooij, Michael Moutoussisa, Ian Goodyer, Ed Bullmore, Peter Jones, 
#Peter Fonagy, NSPN Consortium, Ulman Lindenberger & Raymond J. Dolan                                                         

#The original code was written by Rogier A. Kievit (rogier.kievit@mrc-cbu.cam.ac.uk), 30 January 2017.
#It may be used, (re)shared and modified freely under a CC-BY license 

#This script simulates, then saves, then fits, data for a univariate Latent Change Score model.

# Select data

data <- df %>% dplyr::select(
  id,
  autonomous_T1 = PA_autonomous_T1,
  autonomous_T2 = PA_autonomous_T3 # In the study, there was a mid-intervention T2, but for intervention group only
  )

# Fit the Univariate Latent Change Score model
ULCS <- '
autonomous_T2 ~  1*autonomous_T1     # Fixed regression of T2 on T1
d_autonomous1 =~ 1*autonomous_T2     # Fixed regression of d_autonomous1 on autonomous_T2
autonomous_T2 ~  0*1                 # This line constrains the intercept of autonomous_T2 to 0
autonomous_T2 ~~ 0*autonomous_T2     # This fixes the variance of the autonomous_T2 to 0 

d_autonomous1 ~  1                   # This estimates the intercept of the change scores 
autonomous_T1 ~  1                   # This estimates the intercept of autonomous_T1 
d_autonomous1 ~~ d_autonomous1       # This estimates the variance of the change scores 
autonomous_T1 ~~ autonomous_T1       # This estimates the variance of autonomous_T1 
d_autonomous1 ~ autonomous_T1        # This estimates the self-feedback parameter
'

fitULCS <- lavaan::lavaan(ULCS, data = data, estimator='mlr', fixed.x=FALSE, missing='fiml')
lavaan::summary(fitULCS, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)

lavaan::coef(fitULCS) 

# Plot raw scores 
df %>% dplyr::select(
  id,
  intervention,
  T1 = PA_autonomous_T1,
  T2 = PA_autonomous_T3 # In the study, there was a mid-intervention T2, but for intervention group only
  ) %>% 
  mutate(intervention = factor(intervention, labels = c("Control group", "Intervention group"))) %>% 
  gather(variable, value, -id, -intervention) %>% 
  na.omit(.) %>% 
ggplot(aes(variable, value, group=id)) +
  geom_point(col = 'dodgerblue', size = 3, alpha = .2) +
  geom_line(col = 'dodgerblue', alpha = .2) +
  ggtitle('Univariate Latent Change Score model') + 
  ylab('Autonomous motivation scores') +
  xlab('Time points') + 
  facet_wrap("intervention")

# Plot the SEM model
semPlot::semPaths(fitULCS, "std", edge.label.cex = 1, curvePivot = TRUE, layout = "tree",
                  color = list(lat = viridis::viridis(3, begin = 0.3)[1], 
                               man = viridis::viridis(3, begin = 0.3)[2], 
                               int = viridis::viridis(3, begin = 0.3)[3]))

# Fit model with variance of change constrained at zero, leads to a non positive definite covariance matrix. 

# ULCS_d0 <- '
# autonomous_T2 ~  1*autonomous_T1     # Fixed regression of T2 on T1
# d_autonomous1 =~ 1*autonomous_T2     # Fixed regression of d_autonomous1 on autonomous_T2
# autonomous_T2 ~  0*1                 # This line constrains the intercept of autonomous_T2 to 0
# autonomous_T2 ~~ 0*autonomous_T2     # This fixes the variance of the autonomous_T2 to 0 
# 
# d_autonomous1 ~  1                   # This estimates the intercept of the change scores 
# autonomous_T1 ~  1                   # This estimates the intercept of autonomous_T1 
# d_autonomous1 ~~ 0*d_autonomous1      # NOW ZERO - This estimates the variance of the change scores 
# autonomous_T1 ~~ autonomous_T1       # This estimates the variance of autonomous_T1 
# d_autonomous1 ~ autonomous_T1        # This estimates the self-feedback parameter
# '
# 
# fitULCS_d0 <- lavaan::lavaan(ULCS_d0, data = data, estimator='mlr', fixed.x=FALSE, missing='fiml')
# lavaan::summary(fitULCS_d0, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)

```

We can observe, that high starting scores on autonomous motivation lead to smaller changes and vice versa, understandably due to ceiling effects in the data. The intercept for change is positive, so there was a general trend of increasing scores on the measure.

How to interpret the path from d_1 to a_T2?

# Multiple indicators for automous

## Plot raw scores 

```{r}

drawit <- function(regulation) {
pd <- position_dodge(0.4) # see: https://stackoverflow.com/questions/39533456/r-how-to-jitter-both-geom-line-and-geom-point-in-ggplot2-linegraph

# Show change scores; see https://stackoverflow.com/questions/50181772/line-color-and-width-by-slope-in-ggplot2

data_MILCS %>% 
  dplyr::mutate(intervention = factor(intervention, labels = c("Control group", "Intervention group"))) %>% 
  tidyr::gather(variable, value, -id, -girl, -intervention) %>% 
  tidyr::separate(variable, c("item", "time"), sep = "_T") %>% 
  dplyr::mutate(value = jitter(value, amount = 0.1)) %>% # Y-axis jitter to make points more readable
  group_by(id, item) %>% 
  mutate(slope = (value[time==2] - value[time==1])/(2-1)) %>% 
  dplyr::filter(stringr::str_detect(item, regulation)) %>% # Search the variable "item" for string given by the regulation (e.g. "intrinsic") and keep only those
  # dplyr::filter(intervention == intervention_allocation) %>%
  na.omit(.) %>% 
ggplot(aes(x = time, y = value, group = id)) +
  geom_point(size = 1, alpha = .2, position = pd) +
  geom_line(aes(color = slope), alpha = .2, size = 1.5, position = pd) +
  scale_color_viridis_c(option = "inferno") +
  # ggtitle(paste0('Multiple indicator LCS model: ', regulation)) + 
  ylab(paste0(regulation, ' regulation scores')) +
  xlab('Time points') + 
  facet_wrap(c("intervention", "item"), nrow = 2) +
  theme(legend.position="none", 
        strip.text = element_blank(), # comment out to show labels; https://stackoverflow.com/questions/32426951/in-ggplot2-and-facet-wrap-how-to-remove-all-margins-and-padding-yet-keep-strip
        plot.caption = element_text(size = 8, hjust = 0)) + 
  labs(caption = "Top row for control group, lower row for intervention. Items in columns ordered from left to right, starting with 1.")
  }

drawit("intrinsic")

# To plot all of the regulations in 6-panel plots:
for (i in c("integrated", "identified", "intrinsic")) {
print(drawit(regulation = i))
}

# For single-item comparison between intervention and control: 
for (i in c("integrated", "identified", "intrinsic")) {
for (j in c(1:3)) {
print(drawit(regulation = paste0(i, "_0", j)))
}}
```


```{r multiple-indicators-model}
# Select data

data_MILCS <- df %>% dplyr::select(
  id,
  girl,
  intervention,
  PA_amotivation_02_T1,
  PA_amotivation_01_T1,
  PA_amotivation_03_T1,
  PA_amotivation_04_T1,
  PA_extrinsic_01_T1,
  PA_extrinsic_02_T1,
  PA_extrinsic_03_T1,
  PA_introjected_01_T1,
  PA_introjected_02_T1,
  PA_identified_01_T1,
  PA_identified_02_T1,
  PA_identified_03_T1,
  PA_integrated_01_T1,
  PA_integrated_02_T1,
  PA_integrated_03_T1,
  PA_intrinsic_01_T1,
  PA_intrinsic_02_T1,
  PA_intrinsic_03_T1,
  PA_amotivation_02_T3,
  PA_amotivation_01_T3,
  PA_amotivation_03_T3,
  PA_amotivation_04_T3,
  PA_extrinsic_01_T3,
  PA_extrinsic_02_T3,
  PA_extrinsic_03_T3,
  PA_introjected_01_T3,
  PA_introjected_02_T3,
  PA_identified_01_T3,
  PA_identified_02_T3,
  PA_identified_03_T3,
  PA_integrated_01_T3,
  PA_integrated_02_T3,
  PA_integrated_03_T3,
  PA_intrinsic_01_T3,
  PA_intrinsic_02_T3,
  PA_intrinsic_03_T3
  )

# Remove "PA_" from variable names for nicer plotting:
names(data_MILCS) <- gsub("PA_", "", names(data_MILCS))

# Change "_T3" to "_T2" for clarity
names(data_MILCS) <- gsub("_T3", "_T2", names(data_MILCS))

MILCS <- '
# This specifies the measurement model for autonomous_T1:
autonomous_T1 =~ 1 * identified_01_T1 + identified_02_T1 + identified_03_T1 +
                     integrated_01_T1 + integrated_02_T1 + integrated_03_T1 +
                     intrinsic_01_T1 + intrinsic_02_T1 + intrinsic_03_T1  

# This specifies the measurement model for autonomous_T2 with the equality constrained factor loadings:
autonomous_T2 =~ 1 * identified_01_T2 + 
                    equal("autonomous_T1 =~ identified_02_T1") * identified_02_T2 +
                    equal("autonomous_T1 =~ identified_03_T1") * identified_03_T2 +
                    equal("autonomous_T1 =~ integrated_01_T1") * integrated_01_T2 + 
                    equal("autonomous_T1 =~ integrated_02_T1") * integrated_02_T2 +
                    equal("autonomous_T1 =~ integrated_03_T1") * integrated_03_T2 +
                    equal("autonomous_T1 =~ intrinsic_01_T1") * intrinsic_01_T2 + 
                    equal("autonomous_T1 =~ intrinsic_02_T1") * intrinsic_02_T2 +
                    equal("autonomous_T1 =~ intrinsic_03_T1") * intrinsic_03_T2

autonomous_T2 ~ 1*autonomous_T1     # Fixed regression of autonomous_T2 on autonomous_T1
d_aut1 =~ 1*autonomous_T2           # Fixed regression of d_aut1 on autonomous_T2
autonomous_T2 ~ 0*1                 # This line constrains the intercept of autonomous_T2 to 0
autonomous_T2 ~~ 0*autonomous_T2    # This fixes the variance of the autonomous_T2 to 0 

d_aut1 ~ 1                          # This estimates the intercept of the change score 
autonomous_T1 ~  1                  # This estimates the intercept of autonomous_T1 
d_aut1 ~~  d_aut1                   # This estimates the variance of the change scores 
autonomous_T1 ~~ autonomous_T1      # This estimates the variance of the autonomous_T1 
d_aut1 ~ autonomous_T1              # This estimates the self-feedback parameter

# This allows residual variances on indicators:
identified_01_T1 ~~ identified_01_T1
identified_02_T1 ~~ identified_02_T1
identified_03_T1 ~~ identified_03_T1
integrated_01_T1 ~~ integrated_01_T1
integrated_02_T1 ~~ integrated_02_T1
integrated_03_T1 ~~ integrated_03_T1
intrinsic_01_T1 ~~ intrinsic_01_T1
intrinsic_02_T1 ~~ intrinsic_02_T1
intrinsic_03_T1 ~~ intrinsic_03_T1

# This allows residual covariances across of a single indicator across T1 and T2
identified_01_T1 ~~ identified_01_T2
identified_02_T1 ~~ identified_02_T2
identified_03_T1 ~~ identified_03_T2
integrated_01_T1 ~~ integrated_01_T2
integrated_02_T1 ~~ integrated_02_T2
integrated_03_T1 ~~ integrated_03_T2
intrinsic_01_T1 ~~ intrinsic_01_T2
intrinsic_02_T1 ~~ intrinsic_02_T2
intrinsic_03_T1 ~~ intrinsic_03_T2

# This allows residual variance on indicators at T2 
identified_01_T2 ~~ equal("identified_01_T1 ~~ identified_01_T1") * identified_01_T2
identified_02_T2 ~~ equal("identified_02_T1 ~~ identified_02_T1") * identified_02_T2
identified_03_T2 ~~ equal("identified_03_T1 ~~ identified_03_T1") * identified_03_T2
integrated_01_T2 ~~ equal("integrated_01_T1 ~~ integrated_01_T1") * integrated_01_T2
integrated_02_T2 ~~ equal("integrated_02_T1 ~~ integrated_02_T1") * integrated_02_T2
integrated_03_T2 ~~ equal("integrated_03_T1 ~~ integrated_03_T1") * integrated_03_T2
intrinsic_01_T2 ~~ equal("intrinsic_01_T1 ~~ intrinsic_01_T1") * intrinsic_01_T2
intrinsic_02_T2 ~~ equal("intrinsic_02_T1 ~~ intrinsic_02_T1") * intrinsic_02_T2
intrinsic_03_T2 ~~ equal("intrinsic_03_T1 ~~ intrinsic_03_T1") * intrinsic_03_T2

# This constrains the first intercept of indicator to 0 at T1, estimates others
identified_01_T1 ~ 0*1                 
identified_02_T1 ~ 1
identified_03_T1 ~ 1
integrated_01_T1 ~ 1
integrated_02_T1 ~ 1
integrated_03_T1 ~ 1
intrinsic_01_T1 ~ 1
intrinsic_02_T1 ~ 1
intrinsic_03_T1 ~ 1

# Same with t2, except the value is predicted by the intercept of the previous time point
identified_01_T2 ~ 0 * 1
identified_02_T2 ~ equal("identified_02_T1 ~ 1") * 1
identified_03_T2 ~ equal("identified_03_T1 ~ 1") * 1
integrated_01_T2 ~ equal("integrated_01_T1 ~ 1") * 1
integrated_02_T2 ~ equal("integrated_02_T1 ~ 1") * 1
integrated_03_T2 ~ equal("integrated_03_T1 ~ 1") * 1
intrinsic_01_T2 ~ equal("intrinsic_01_T1 ~ 1") * 1
intrinsic_02_T2 ~ equal("intrinsic_02_T1 ~ 1") * 1
intrinsic_03_T2 ~ equal("intrinsic_03_T1 ~ 1") * 1
'

fitMILCS <- lavaan::lavaan(MILCS, 
                           data = data_MILCS, 
                           group = 'intervention', 
                           estimator='mlr', 
                           fixed.x = FALSE, 
                           missing='fiml')

lavaan::summary(fitMILCS, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)

lavaan::coef(fitMILCS) 

# Plot the SEM model

# Plot the SEM model
semPlot::semPaths(fitMILCS, 
                  what = "std",
                  ask = FALSE,
                  label.cex = .6, 
                  label.scale = FALSE,
                  edge.label.cex = 0.75, 
                  layout = "tree",
                  intercepts = FALSE,
                  color = list(lat = viridis::viridis(3, begin = 0.3)[1], 
                               man = viridis::viridis(3, begin = 0.3)[2], 
                               int = viridis::viridis(3, begin = 0.3)[3]))

```

```{r slopePlot}

# Plot raw scores 
drawit <- function(regulation) {
pd <- position_dodge(0.4) # see: https://stackoverflow.com/questions/39533456/r-how-to-jitter-both-geom-line-and-geom-point-in-ggplot2-linegraph

# Show change scores; see https://stackoverflow.com/questions/50181772/line-color-and-width-by-slope-in-ggplot2

data_MILCS %>% 
  dplyr::mutate(intervention = factor(intervention, labels = c("Control group", "Intervention group"))) %>% 
  tidyr::gather(variable, value, -id, -girl, -intervention) %>% 
  tidyr::separate(variable, c("item", "time"), sep = "_T") %>% 
  dplyr::mutate(value = jitter(value, amount = 0.1)) %>% # Y-axis jitter to make points more readable
  group_by(id, item) %>% 
  mutate(slope = (value[time==2] - value[time==1])/(2-1)) %>% 
  dplyr::filter(stringr::str_detect(item, regulation)) %>% # Search the variable "item" for string given by the regulation (e.g. "intrinsic") and keep only those
  # dplyr::filter(intervention == intervention_allocation) %>%
  na.omit(.) %>% 
ggplot(aes(x = time, y = value, group = id)) +
  geom_point(size = 1, alpha = .2, position = pd) +
  geom_line(aes(color = slope), alpha = .2, size = 1.5, position = pd) +
  scale_color_viridis_c(option = "inferno") +
  # ggtitle(paste0('Multiple indicator LCS model: ', regulation)) + 
  ylab(paste0(regulation, ' regulation scores')) +
  xlab('Time points') + 
  facet_wrap(c("intervention", "item"), nrow = 2) +
  theme(legend.position="none", 
        strip.text = element_blank(), # comment out to show labels; https://stackoverflow.com/questions/32426951/in-ggplot2-and-facet-wrap-how-to-remove-all-margins-and-padding-yet-keep-strip
        plot.caption = element_text(size = 8, hjust = 0)) + 
  labs(caption = "Top row for control group, lower row for intervention. Items in columns ordered from left to right, starting with 1.")
  }

drawit("intrinsic")

# To plot all of the regulations in 6-panel plots:
for (i in c("integrated", "identified", "intrinsic")) {
print(drawit(regulation = i))
}

# For single-item comparison between intervention and control: 
for (i in c("integrated", "identified", "intrinsic")) {
for (j in c(1:3)) {
print(drawit(regulation = paste0(i, "_0", j)))
}}

# To check out observed means:
# df %>% select(intervention, contains("diff")) %>% select(intervention, matches("identified|intrinsic|integrated")) %>% group_by(intervention) %>% summarise_all(mean, na.rm = TRUE)
```


## Separate regulations 

```{r}
# Select data

data_MILCS <- df %>% dplyr::select(
  id,
  girl,
  intervention,
  PA_amotivation_02_T1,
  PA_amotivation_01_T1,
  PA_amotivation_03_T1,
  PA_amotivation_04_T1,
  PA_extrinsic_01_T1,
  PA_extrinsic_02_T1,
  PA_extrinsic_03_T1,
  PA_introjected_01_T1,
  PA_introjected_02_T1,
  PA_identified_01_T1,
  PA_identified_02_T1,
  PA_identified_03_T1,
  PA_integrated_01_T1,
  PA_integrated_02_T1,
  PA_integrated_03_T1,
  PA_intrinsic_01_T1,
  PA_intrinsic_02_T1,
  PA_intrinsic_03_T1,
  PA_amotivation_02_T3,
  PA_amotivation_01_T3,
  PA_amotivation_03_T3,
  PA_amotivation_04_T3,
  PA_extrinsic_01_T3,
  PA_extrinsic_02_T3,
  PA_extrinsic_03_T3,
  PA_introjected_01_T3,
  PA_introjected_02_T3,
  PA_identified_01_T3,
  PA_identified_02_T3,
  PA_identified_03_T3,
  PA_integrated_01_T3,
  PA_integrated_02_T3,
  PA_integrated_03_T3,
  PA_intrinsic_01_T3,
  PA_intrinsic_02_T3,
  PA_intrinsic_03_T3
  )

# Remove "PA_" from variable names for nicer plotting:
names(data_MILCS) <- gsub("PA_", "", names(data_MILCS))

# Change "_T3" to "_T2" for clarity
names(data_MILCS) <- gsub("_T3", "_T2", names(data_MILCS))

MILCS <- '
# This specifies the measurement models for T1:
intrinsic_T1  =~ 1 * intrinsic_01_T1 + intrinsic_02_T1 + intrinsic_03_T1  
identified_T1 =~ 1 * identified_01_T1 + identified_02_T1 + identified_03_T1
#integrated_T1 =~ 1 * integrated_01_T1 + integrated_02_T1 + integrated_03_T1

# This specifies the measurement models for T2 with the equality constrained factor loadings:
intrinsic_T2  =~ 1 * intrinsic_01_T2 + 
                 equal("intrinsic_T1 =~ intrinsic_02_T1") * intrinsic_02_T2 +
                 equal("intrinsic_T1 =~ intrinsic_03_T1") * intrinsic_03_T2
identified_T2  =~ 1 * identified_01_T2 + 
                 equal("identified_T1 =~ identified_02_T1") * identified_02_T2 +
                 equal("identified_T1 =~ identified_03_T1") * identified_03_T2
#integrated_T2  =~ 1 * integrated_01_T2 + 
#                 equal("integrated_T1 =~ integrated_02_T1") * integrated_02_T2 +
#                 equal("integrated_T1 =~ integrated_03_T1") * integrated_03_T2

intrinsic_T2 ~ 1*intrinsic_T1       # Fixed regression of intrinsic_T2 on intrinsic_T1
d_intrinsic1 =~ 1*intrinsic_T2      # Fixed regression of d_intrinsic1 on intrinsic_T2
intrinsic_T2 ~ 0*1                  # This line constrains the intercept of intrinsic_T2 to 0
intrinsic_T2 ~~ 0*intrinsic_T2      # This fixes the variance of the intrinsic_T2 to 0 

d_intrinsic1 ~ 1                    # This estimates the intercept of the change score 
intrinsic_T1 ~  1                   # This estimates the intercept of intrinsic_T1 
d_intrinsic1 ~~  d_intrinsic1       # This estimates the variance of the change scores 
intrinsic_T1 ~~ intrinsic_T1        # This estimates the variance of the intrinsic_T1 
d_intrinsic1 ~ intrinsic_T1         # This estimates the self-feedback parameter

#integrated_T2 ~ 1*integrated_T1     # Fixed regression of integrated_T2 on integrated_T1
#d_integrated1 =~ 1*integrated_T2    # Fixed regression of d_integrated1 on integrated_T2
#integrated_T2 ~ 0*1                 # This line constrains the intercept of integrated_T2 to 0
#integrated_T2 ~~ 0*integrated_T2    # This fixes the variance of the integrated_T2 to 0 

#d_integrated1 ~ 1                   # This estimates the intercept of the change score 
#integrated_T1 ~  1                  # This estimates the intercept of integrated_T1 
#d_integrated1 ~~  d_integrated1     # This estimates the variance of the change scores 
#integrated_T1 ~~ integrated_T1      # This estimates the variance of the integrated_T1 
#d_integrated1 ~ integrated_T1       # This estimates the self-feedback parameter

identified_T2 ~ 1*identified_T1     # Fixed regression of identified_T2 on identified_T1
d_identified1 =~ 1*identified_T2    # Fixed regression of d_identified1 on identified_T2
identified_T2 ~ 0*1                 # This line constrains the intercept of identified_T2 to 0
identified_T2 ~~ 0*identified_T2    # This fixes the variance of the identified_T2 to 0 

d_identified1 ~ 1                   # This estimates the intercept of the change score 
identified_T1 ~  1                  # This estimates the intercept of identified_T1 
d_identified1 ~~  d_identified1     # This estimates the variance of the change scores 
identified_T1 ~~ identified_T1      # This estimates the variance of the identified_T1 
d_identified1 ~ identified_T1       # This estimates the self-feedback parameter

# This allows residual variances on indicators:
identified_01_T1 ~~ identified_01_T1
identified_02_T1 ~~ identified_02_T1
identified_03_T1 ~~ identified_03_T1
#integrated_01_T1 ~~ integrated_01_T1
#integrated_02_T1 ~~ integrated_02_T1
#integrated_03_T1 ~~ integrated_03_T1
intrinsic_01_T1 ~~ intrinsic_01_T1
intrinsic_02_T1 ~~ intrinsic_02_T1
intrinsic_03_T1 ~~ intrinsic_03_T1

# This allows residual covariances across of a single indicator across T1 and T2
identified_01_T1 ~~ identified_01_T2
identified_02_T1 ~~ identified_02_T2
identified_03_T1 ~~ identified_03_T2
#integrated_01_T1 ~~ integrated_01_T2
#integrated_02_T1 ~~ integrated_02_T2
#integrated_03_T1 ~~ integrated_03_T2
intrinsic_01_T1 ~~ intrinsic_01_T2
intrinsic_02_T1 ~~ intrinsic_02_T2
intrinsic_03_T1 ~~ intrinsic_03_T2

# This allows residual variance on indicators at T2 
identified_01_T2 ~~ equal("identified_01_T1 ~~ identified_01_T1") * identified_01_T2
identified_02_T2 ~~ equal("identified_02_T1 ~~ identified_02_T1") * identified_02_T2
identified_03_T2 ~~ equal("identified_03_T1 ~~ identified_03_T1") * identified_03_T2
#integrated_01_T2 ~~ equal("integrated_01_T1 ~~ integrated_01_T1") * integrated_01_T2
#integrated_02_T2 ~~ equal("integrated_02_T1 ~~ integrated_02_T1") * integrated_02_T2
#integrated_03_T2 ~~ equal("integrated_03_T1 ~~ integrated_03_T1") * integrated_03_T2
intrinsic_01_T2 ~~ equal("intrinsic_01_T1 ~~ intrinsic_01_T1") * intrinsic_01_T2
intrinsic_02_T2 ~~ equal("intrinsic_02_T1 ~~ intrinsic_02_T1") * intrinsic_02_T2
intrinsic_03_T2 ~~ equal("intrinsic_03_T1 ~~ intrinsic_03_T1") * intrinsic_03_T2

# This constrains the first intercept of indicator to 0 at T1, estimates others
identified_01_T1 ~ 0*1                 
identified_02_T1 ~ 1
identified_03_T1 ~ 1
#integrated_01_T1 ~ 0*1
#integrated_02_T1 ~ 1
#integrated_03_T1 ~ 1
intrinsic_01_T1 ~ 0*1
intrinsic_02_T1 ~ 1
intrinsic_03_T1 ~ 1

# Same with t2, except the value is predicted by the intercept of the previous time point
identified_01_T2 ~ 0 * 1
identified_02_T2 ~ equal("identified_02_T1 ~ 1") * 1
identified_03_T2 ~ equal("identified_03_T1 ~ 1") * 1
#integrated_01_T2 ~ 0 * 1
#integrated_02_T2 ~ equal("integrated_02_T1 ~ 1") * 1
#integrated_03_T2 ~ equal("integrated_03_T1 ~ 1") * 1
intrinsic_01_T2 ~ 0 * 1
intrinsic_02_T2 ~ equal("intrinsic_02_T1 ~ 1") * 1
intrinsic_03_T2 ~ equal("intrinsic_03_T1 ~ 1") * 1

# Estimate covariance between T1 variables
#intrinsic_T1 ~~ integrated_T1
intrinsic_T1 ~~ identified_T1
#integrated_T1 ~~ identified_T1

# Estimate covariance between changes
#d_intrinsic1 ~~ d_integrated1
d_intrinsic1 ~~ d_identified1
#d_integrated1 ~~ d_identified1
'

fitMILCS_individualRegulations <- lavaan::lavaan(MILCS, data = data_MILCS, estimator='mlr', fixed.x = FALSE, missing='fiml', group='intervention')
lavaan::summary(fitMILCS_individualRegulations, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)

lavaan::summary(fitMILCS_individualRegulations, fit.measures=FALSE, standardized=TRUE, rsquare=FALSE)

lavaan::coef(fitMILCS_individualRegulations) 

lavaan::fitmeasures(fitMILCS_individualRegulations)
cbind(m1 = lavaan::inspect(fitMILCS_individualRegulations, 'fit.measures') %>% round(., 2), m2 = lavaan::inspect(fitMILCS, 'fit.measures') %>% round(., 2))

# Plot the SEM model
semPlot::semPaths(fitMILCS_individualRegulations, 
                  what = "std",
                  ask = FALSE,
                  label.cex = .6, 
                  label.scale = FALSE,
                  edge.label.cex = 0.75, 
                  layout = "tree",
                  intercepts = FALSE,
                  color = list(lat = viridis::viridis(3, begin = 0.3)[1], 
                               man = viridis::viridis(3, begin = 0.3)[2], 
                               int = viridis::viridis(3, begin = 0.3)[3]))

lavaan::modificationindices(fitMILCS_individualRegulations) %>% 
  arrange(desc(mi))

lavaan::inspect(fitMILCS_individualRegulations, "cov.lv")
```

# Coupling of Autonomous motivation and BCTs

```{r aut-bct-coupling}
# The model in this script is originally part of the manuscript 
#'Developmental cognitive neuroscience using Latent Change Score models: A tutorial and applications'
#Rogier A. Kievit, Andreas M. Brandmaier, Gabriel Ziegler, Anne-Laura van Harmelen, 
#Susanne de Mooij, Michael Moutoussisa, Ian Goodyer, Ed Bullmore, Peter Jones, 
#Peter Fonagy, NSPN Consortium, Ulman Lindenberger & Raymond J. Dolan                                                         
# Code was originally written by Rogier A. Kievit (rogier.kievit@mrc-cbu.cam.ac.uk), 30 January 2017.
# It may be used, (re)shared and modified freely under a CC-BY license 

data_BLCS <- df %>% dplyr::select(
  intervention,
  Autonomous_T1 = PA_autonomous_T1,
  Autonomous_T2 = PA_autonomous_T3,
  frqbct_T1 = PA_frqbct_T1,
  frqbct_T2 = PA_frqbct_T3,
  agrbct_T1 = PA_agrbct_T1,
  agrbct_T2 = PA_agrbct_T3) %>% 
  rowwise() %>% 
  dplyr::mutate(BCTs_T1 = mean(c(frqbct_T1, agrbct_T1), na.rm = TRUE),
                BCTs_T2 = mean(c(frqbct_T2, agrbct_T2), na.rm = TRUE)) %>% 
  dplyr::select(-contains("frq"), -contains("agr"))


#Fit the Bivariate Latent Change Score model to simulated data
BLCS<-'

Autonomous_T2 ~ 1 * Autonomous_T1     # This parameter regresses Autonomous_T2 perfectly on Autonomous_T1
d_Autonomous1 =~ 1 * Autonomous_T2     # This defines the latent change score factor as measured perfectly by scores on Autonomous_T2
d_Autonomous1 ~ 1             # This estimates the intercept of the change score 
Autonomous_T1 ~  1           # This estimates the intercept of Autonomous_T1 
Autonomous_T2 ~ 0 * 1          # This constrains the intercept of Autonomous_T2 to 0

BCTs_T2 ~ 1 * BCTs_T1     # This parameter regresses BCTs_T2 perfectly on BCTs_T1
d_BCTs1 =~ 1 * BCTs_T2     # This defines the latent change score factor as measured perfectly by scores on BCTs_T2
BCTs_T2 ~ 0 * 1          # This line constrains the intercept of BCTs_T2 to 0
BCTs_T2 ~~ 0 * BCTs_T2    # This fixes the variance of the BCTs_T1 to 0  

d_Autonomous1 ~~  d_Autonomous1       # This estimates the variance of the change scores
Autonomous_T1 ~~   Autonomous_T1    # This estimates the variance of the Autonomous_T1 
Autonomous_T2 ~~ 0 * Autonomous_T2    # This fixes the variance of the Autonomous_T2 to 0  

d_BCTs1 ~ 1             # This estimates the intercept of the change score 
BCTs_T1 ~ 1            # This estimates the intercept of BCTs_T1 
d_BCTs1 ~~ d_BCTs1        # This estimates the variance of the change scores 
BCTs_T1 ~~ BCTs_T1      # This estimates the variance of BCTs_T1 

d_BCTs1 ~ Autonomous_T1 + BCTs_T1   # This estimates the COG to NEU coupling parameter and the COG to COG self-feedback
d_Autonomous1 ~ BCTs_T1 + Autonomous_T1   # This estimates the NEU to COG coupling parameter and the NEU to NEU self-feedback

Autonomous_T1 ~~ BCTs_T1     # This estimates the Autonomous_T1 BCTs_T1 covariance
d_Autonomous1 ~~ d_BCTs1          # This estimates the d_Autonomous and d_BCTs covariance
'

fitBLCS <- lavaan::lavaan(BLCS, 
                          data = data_BLCS, 
                          estimator = 'mlr', 
                          fixed.x = FALSE,
                          group = "intervention",
                          missing = 'fiml')

lavaan::summary(fitBLCS, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)

semPlot::semPaths(fitBLCS, 
                  what = "std",
                  ask = FALSE,
                  label.cex = .6, 
                  label.scale = FALSE,
                  edge.label.cex = 0.75, 
                  layout = "tree2",
                  intercepts = TRUE,
                  color = list(lat = viridis::viridis(3, begin = 0.3)[1], 
                               man = viridis::viridis(3, begin = 0.3)[2], 
                               int = viridis::viridis(3, begin = 0.3)[3]))



```

```{r}
#This MODIFIED FROM https://osf.io/ch3rf/ 
#'Developmental cognitive neuroscience using Latent Change Score models: A tutorial and applications'
#Rogier A. Kievit, Andreas M. Brandmaier, Gabriel Ziegler, Anne-Laura van Harmelen, 
#Susanne de Mooij, Michael Moutoussisa, Ian Goodyer, Ed Bullmore, Peter Jones, 
#Peter Fonagy, NSPN Consortium, Ulman Lindenberger & Raymond J. Dolan                                                         
#Original code was written by Rogier A. Kievit (rogier.kievit@mrc-cbu.cam.ac.uk), 30 January 2017.
#It may be used, (re)shared and modified freely under a CC-BY license 

#Fix sample size
samplesize<-500

#Simulate data for a Univariate Latent Change Score model. 
MG_ULCS_simulate<-'

#####     The following lines specify the core assumptions of the LCS 
#####     and should not generally be modified

COG_T2 ~ 1*COG_T1       # Fixed regression of COG_T2 on COG_T1
dCOG1 =~ 1*COG_T2       # Fixed regression of dCOG1 on COG_T2
COG_T2 ~ 0*1            # This line constrains the intercept of COG_T2 to 0
COG_T2 ~~ 0*COG_T2      # This fixes the variance of the COG_T2 to 0  


###### The following five parameters will be estimated in the model. 
###### Values can be modified manually to examine the effect on the model

dCOG1 ~ c(4,8)*1        # This fixes the change score intercept to 4 and 8 for two groups
COG_T1 ~ 50*1           # This fixes the intercept of COG_T1 to 50. 

dCOG1 ~~ c(4,2)*dCOG1   # This fixes the change scores variance to 4 & 2 
COG_T1 ~~ 8*COG_T1      # This fixes the variance of the COG_T1 to 8

dCOG1~-0.05*COG_T1      # This fixes the self-feedback parameter to -0.05

'

#Simulate data
set.seed(1234)
simdatMG_ULCS<-lavaan::simulateData(MG_ULCS_simulate,sample.nobs = c(.5*samplesize,.5*samplesize),meanstructure = T) #Simulate data
colMeans(simdatMG_ULCS) #sanity check the means

#Update group to factor for further use
simdatMG_ULCS$group<-as.factor(simdatMG_ULCS$group)
levels(simdatMG_ULCS$group)<-c('Group A', 'Group B')

#Fit the Univariate Latent Change Score model to simulated data
MG_ULCS<-'

COG_T2 ~ 1*COG_T1       # Fixed regression of COG_T2 on COG_T1
dCOG1 =~ 1*COG_T2       # Fixed regression of dCOG1 on COG_T2
COG_T2 ~ 0*1            # This line constrains the intercept of COG_T2 to 0
COG_T2 ~~ 0*COG_T2      # This fixes the variance of the COG_T2 to 0  

COG_T1 ~  1             # This estimates the intercept of COG_T1 

dCOG1 ~~  dCOG1         # This estimates the variance of the change scores
COG_T1 ~~   COG_T1      # This estimates the variance of the COG_T1 

dCOG1~COG_T1            # This estimates the self-feedback parameter

'

fitMG_ULCS <- lavaan::lavaan(MG_ULCS, data=simdatMG_ULCS, estimator='mlr',fixed.x=FALSE,group='group',missing='fiml')
summary(fitMG_ULCS, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)

semPlot::semPaths(fitMG_ULCS, "std", label.cex = .6, label.scale = FALSE, edge.label.cex = 0.75, layout = "tree",
                  intercepts = FALSE,
                  layoutSplit = TRUE,
                  color = list(lat = viridis::viridis(3, begin = 0.3)[1], 
                               man = viridis::viridis(3, begin = 0.3)[2], 
                               int = viridis::viridis(3, begin = 0.3)[3]))

```

```{r}
  # identified =~ PA_identified_01_T1 + PA_identified_02_T1 + PA_identified_03_T1
  # integrated =~ PA_integrated_01_T1 + PA_integrated_02_T1 + PA_integrated_03_T1
  # intrinsic =~ PA_intrinsic_01_T1 + PA_intrinsic_02_T1 + PA_intrinsic_03_T1
  # introjected =~ PA_introjected_01_T1 + PA_introjected_02_T1
  # extrinsic =~ PA_extrinsic_01_T1 + PA_extrinsic_02_T1 + PA_extrinsic_03_T1 
  # amotivation =~ PA_amotivation_01_T1 + PA_amotivation_02_T1 + PA_amotivation_03_T1 + PA_amotivation_04_T1
```

# Mediation 

Seems like autonomous motivation predicts activity measured with either self-report or accelerometry, but intervention won't predict autonomous motivation.

```{r mediation}
data_mediation <- df %>% dplyr::select(intervention, X = PA_agrbct_T1, M = PA_autonomous_T3, Y = mvpaAccelerometer_T3)

model <- ' # direct effect
             Y ~ c*X
           # mediator
             M ~ a*X
             Y ~ b*M
           # indirect effect (a*b)
             ab := a*b
           # total effect
             total := c + (a*b)
         '
fit <- lavaan::sem(model, data = data_mediation, group = "intervention")
lavaan::summary(fit)


semPlot::semPaths(fit, "std", label.cex = .6, label.scale = FALSE, edge.label.cex = 0.75, layout = "tree",
                  intercepts = FALSE,
                  layoutSplit = FALSE,
                  ask = FALSE,
                  color = list(lat = viridis::viridis(3, begin = 0.3)[1], 
                               man = viridis::viridis(3, begin = 0.3)[2], 
                               int = viridis::viridis(3, begin = 0.3)[3]))
```

